High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-01 paper/boneyard.tex
finished robustness testing section, backing up progress

>>>>

For synthetic data where the true underyling dynamic correlations are
known, we are able to directly evaluate how well the recovered
correlations match the ground truth, for different choices of kernel
shape and width.  In contrast, or real-world data (where the ground
truth is not known), we use decoding accuracy to estimate whether a
given set of neural features reliably reflects ongoing stimulus-driven
cognitive processing.  However, under different circumstances,
different classifier properties (e.g., kernel shapes, kernel widths,
classification algorithm, etc.) will give rise to different decoding
accuracies.  We can average over different cross validation group
assignments to improve the stability of the decoding accuracy
assessments (to factor out effects due to particular group
assignments), but

cannot know whether a given

Because decoding accuracy is an indirect
reflection of how much a given set of neural features

We cannot know which choice of kernel most accurately
reflects the ``true'' information content of the data.

For example, a
given kernel might highlight particular temporal aspects of the data
in a way that enhances or diminishes decoding performance.
\textbf{JRM STOPPED HERE}

### 2019-09-01 paper/main.tex
finished robustness testing section, backing up progress

\subsubsection*{Identifying robust decoding results}
For synthetic data where the true underyling dynamic correlations are
known, we are able to directly evaluate how well the recovered
correlations match the ground truth, for different choices of kernel
shape and width.  For real-world data (where the ground truth is not
known), we use decoding accuracy to estimate whether a given set of
neural features reliably reflects ongoing stimulus-driven cognitive
processing.  We cannot know which choice of kernel most accurately
reflects the ``true'' information content of the data.  For example, a
given kernel might highlight particular temporal aspects of the data
in a way that enhances or diminishes decoding performance.
\textbf{JRM STOPPED HERE}

Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,
and 50.

>>>>

\subsubsection*{Identifying robust decoding results}
The temporal decoding procedure we use to estimate which neural
features support ongoing cognitive processing is goverened by many
parameters.  For example, Equation~\ref{eqn:timecorr} requires
defining a kernel function, which can take on different shapes and
widths.  For a fixed set of neural features, each of these parameters
can yield different decoding accuracies.  Further, the best decoding
accuracy for a given timepoint may be reliably achieved by one set of
parameters, whereas the best decoding accuracy for another timepoint
might be reliably achieved by a different set of parameters, and the
best decoding accuracy across \textit{all} timepoints might be
reliably achieved by still another different set of parameters.
Rather than attempting to maximize decoding accuracy, we sought to
discover the trends in the data that were robust to specific
classifier parameters choices.  Specifically, we sought to
characterize how decoding accuracy varied (under different
experimental conditions) as a function of which neural features were
considered.

To identify decoding results that were robust to specific classifier
parameter choices, we repeated our decoding analyses that substituted
in a variety of kernel shapes and widths for
Equation~\ref{eqn:timecorr}.  We examined Gaussian
(Fig.~\ref{fig:kernels}c), Laplace (Fig.~\ref{fig:kernels}d), and
Mexican Hat (Fig.~\ref{fig:kernels}e) kernels, each with widths of 5,
10, 20, and 50 samples.  We then report the average decoding
accuracies across all of these parameter choices.  This enabled us to
(roughly) factor out performance characteristics that were parameter
dependent (within the space of parameters we examined).

\textbf{JRM STOPPED HERE}
